Lens Modeling in \sw

### 2013-11-12 text/tex/results.tex
rearranged figure placement

\subsection{First test T1} \label{sec:tests.t1}

@@

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/006917/input.png}}
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/006917/spaghetti.png}} \\
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/ASW0001hpf/arriv.png}}
%  \subfigure{\includegraphics[width=0.45\textwidth]
%             {fig/sims/ASW0001hpf/extr_points.png}}
  \caption{Examples of Spaghetti input (left top) and modeled arrival time surface (right top) vs reconstructed arrival time surface from simulation parameters (bottom).}
  \label{fig:output_compare}
\end{figure}

@@

\input{tab/auto/_stats}

@@

\subsection{Second test T2} \label{sec:tests.t2}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.80\textwidth]{fig/sims/eR_1.png}
  \caption{\ERf for all models with estimated errors in blue squares, \ERg of simulation in red crosses}
  \label{fig:ER_all_models}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.80\textwidth]{fig/sims/eR_4.png}
  \caption{relative \ERf / \ERg[, sim] for models by volunteers (blue cross), models made by an expert (red cross with offset), including rejected models (green squares); binned per sim.}
  \label{fig:ER_per_sim}
\end{figure}

@@

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/007020/kappa_encl}}
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/007021/kappa_encl}} \\
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/007024/kappa_encl}}
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/007025/kappa_encl}}
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/sims/007022/kappa_encl}}
  \caption{\kenc for models of \asw{0h2m}: 7020 (top left), 7021 (top right), 7024 (mid left), 7025 (mid right) by volunteers and a correct model 7022 (bottom) by an expert.}
  \label{fig:kapenc_compare_faulty}
\end{figure}

>>>>

\subsection{Test of image identification} \label{sec:tests.t1}

@@

@@

@@

\subsection{Test of mass-profile recovery} \label{sec:tests.t2}

@@

@@

@@
